Impact of the High Population Events on Urban Mobility: Who is Affected the Most?

### 2019-12-10 manuscript.Rmd
white_pct

```{r SAR_models}
dc_sar_nontreat <- spautolm(formula = MeanTimeNonTreat ~ med_income + asian_pct + black_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance, data = travel_time_diff, listw = listW, family = "SAR")

dc_sar_treat <- spautolm(formula = MeanTimeTreat ~ med_income + asian_pct + black_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance, data = travel_time_diff, listw = listW, family = "SAR")

@@

```{r}
dc_sar_diff <- spautolm(formula = MeanTimeDiff ~ med_income + asian_pct + black_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance, data = travel_time_diff, listw = listW, family = "SAR")

>>>>

```{r SAR_models}
dc_sar_nontreat <- spautolm(formula = MeanTimeNonTreat ~ med_income + asian_pct + black_pct + white_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance, data = travel_time_diff, listw = listW, family = "SAR")

dc_sar_treat <- spautolm(formula = MeanTimeTreat ~ med_income + asian_pct + black_pct + white_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance, data = travel_time_diff, listw = listW, family = "SAR")

@@

```{r}
dc_sar_diff <- spautolm(formula = MeanTimeDiff ~ med_income + asian_pct + black_pct + white_pct + public_transit_pct + car_transit_pct + n_roads + n_transit + distance , data = travel_time_diff, listw = listW, family = "SAR")
